\huge{Sexual selection improves population fitness: a systematic review and meta-analysis}

### 2019-03-09 Response_to_editorial_requests.Rmd

  All headings are under 60 characters in length, we have some additional Supp Methods in the Supp info but it is more or an appendage to the Supp tables and search terms (which would not nicely format in the main text)

  \item \textit{Please rename the Methods section as "Methods".} \\

  Done

  \item \textit{All Nature Communications manuscripts must include a section titled "Data Availability" as a separate section after the Methods section and before the References.} \\

  We have now ammended this section of the manuscript by seperating data availability and code availability as well as providing the relevent links to the data sources hosted on github.

  \item \textit{We strongly encourage authors to deposit all new data associated with the paper in a persistent repository where they can be freely and enduringly accessed.} \\

  We have chosen to host our data on a github repository alongside all our code and a neatly formatted html with supplementary information in an effort to maximise transparency of our analysis as well as allowing for the data and code to be easily reproduced and built upon by future studies.

  \item \textit{For all studies developing new software or using custom code in the generation or processing of datasets, a statement must be included in the Methods section, under the subheading "Code Availability", indicating whether and how the code can be accessed, including any restrictions to access. This section should also include information on the versions of any software used, if relevant, and any specific variables or parameters used to generate, test, or process the current dataset.} \\

  Done. The Supplementary information has a section at the end with `R Session Information`, which provides details of the attached packages and parameters of the operating system.

  \item \textit{Please add a reference to the source data file in the "Data Availability" section} \\

  Done. The repository now also contains a more extensive 'READ ME', with a description of the repository organisation.

  \item \textit{End notes} \\

  Acknowledgements, Author Contributions and Competing Interests are now found after the references.

  \item \textit{Please update any preprints in the reference list with details of the published paper, if possible.} \\

  We have changed one reference that was a preprint and is now published (Li and Holman 2018).

  \item \textit{Please check whether your manuscript or Supplementary Information contain third-party images, such as figures from the literature, stock photos, clip art or commercial satellite and map data.} \\

  No third-party images are included in the display items.

  \item \textit{Please include a brief title for all figure legends that summarises the whole figure and does not refer to specific panels and Please ensure that figure legend titles are brief - they should not occupy more than one line in the final proof.} \\

  Figure titles are now included and illustrated in bold at the start of the figure legend. They do not occupy more than one line.

  \item \textit{Please include figure legends of up to 350 words, referring to all panels within the figure.} \\

  No figure legends are above 350 words and in all cases all panels are referred to in the legend.

  \item \textit{Data in tables must be free from bold/italic formatting unless this has been clearly defined in the footnote. Tables need to be black and white, fit onto a single A4 portrait page and can contain only one row of column titles. Finally, we are unable to merge cells or include vertical dividing lines or diagonal lines. Please format your tables accordingly.} \\

  Bolding in tables are now clearly defined in the footnotes, the tables are formatted in latex, contain one row of column titles and are in black and white.

  \item \textit{Please ensure that table titles are brief - they should not occupy more than one line in the final proof.} \\

### 2019-03-09 Manuscripts/Manuscript_MetaAnalysis.Rmd
Changes to bib, response to editor and manuscript

The code used to perform this meta-analysis is available on Github (https://justincally.github.io/SexualSelection/). The repository (https://github.com/JustinCally/SexualSelection) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results. \phantomsection

@@

All data are available on Github (https://github.com/JustinCally/SexualSelection).

#Acknowledgements
We are very grateful to Paco Garcia-Gonzalez for sharing a collection of literature that helped to guide our study, and to Tim Connallon for comments on the manuscript.

@@

@@

Table 1: Results for the multilevel meta-analysis model testing the effects of sexual selection on fitness (measured by Hedges' _g_) in different environments and between sexes. Moderator variables whose 95% confidence intervals do not cross zero are shown in bold.

@@

kable(table1, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
  kable_styling(latex_options = c("scale_down", "striped"), full_width = F) %>%
  row_spec(0, bold = TRUE) %>%
  group_rows("REML Model", 1, 6) %>%
  group_rows("Bayesian Model", 7, 12)
```

\vspace{0.75 cm}

Table 2: Hypothesis tests using restricted maximum likelihood (REML) or Bayesian methods, illustrating how sex and environmental stress interact to modulate effect size. Tests whose 95% confidence intervals do not cross zero are shown in bold.

@@

kable(table2, format = "latex", booktabs = T, digits = 2, escape = F) %>% 
  kable_styling(latex_options = c("scale_down"), full_width = F) %>%
  row_spec(0, bold = TRUE) %>%
  collapse_rows(columns = 1:2, latex_hline = "major")
```

@@

![The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness. Overall, effect sizes were more often positive than negative. Predicted average values are presented as a diamond with 95 % CIs for each fitness-relationship category. The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line. Predictions from both Bayesian and REML models can be found in Table S7).\label{forest_plot}](Figures/forest.plot.class.pdf)

![(a) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions. (b) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals. The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Table S12 and S14). Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median.\label{env_sex}](Figures/environment_variance_edit5.pdf)

![Tests of publication bias are mixed and suggest publication bias may be present. (a) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies. (b) No significant correlation exists between journal impact factor and effect size, (c) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias. For (b) and (c) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance). For (a), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99 % CIs for the dataset. The Grey envelopes in (b) and (c) represent the 95 % CI of the linear regression.\label{publication_bias}](Figures/publicationbias.pdf)

![Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets.\label{prisma_flow}](Figures/PRISMA\ Chart.pdf)

>>>>

The code used to perform this meta-analysis is freely available on Github (https://justincally.github.io/SexualSelection/). Here the code is available through a neatly compiled html, with the R Markdown file found within the corresponding github repository:  (https://github.com/JustinCally/SexualSelection).  \phantomsection

@@

All data are freely available on Github (https://github.com/JustinCally/SexualSelection). The repository provides a source data file that was used to create all results, tables and figures. \phantomsection

@@

\newpage
\phantomsection

#Acknowledgements
We are very grateful to Paco Garcia-Gonzalez for sharing a collection of literature that helped to guide our study, and to Tim Connallon for comments on the manuscript.  \phantomsection

#Author contributions  
All authors designed the study; JGC collected the data; JGC and LH conducted the meta-analyses; JGC wrote the first draft of the manuscript; and all authors contributed substantially to all further revisions.  \phantomsection

#Competing interests  
The authors declare no competing interests.

@@

@@

kable(table1, format = "latex", booktabs = T, digits = 2, escape = F, 
      caption = "Multilevel meta-analysis model results") %>% 
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  row_spec(0, bold = TRUE) %>%
  group_rows("REML Model", 1, 6) %>%
  group_rows("Bayesian Model", 7, 12) %>% 
  footnote(symbol_title = "", 
           symbol = c("Moderator variables whose 95\\\\% confidence intervals do not cross zero are shown in bold.", 
                       "Hedges' \\\\textit{g} is the response variable for this model"), 
           threeparttable = T, 
           escape = F)
```

\vspace{0.5 cm}

@@

kable(table2, format = "latex", booktabs = T, digits = 2, escape = F, 
      caption = "Hypothesis tests showing how sex and environmental stress interact to modulate effect size") %>% 
  kable_styling(latex_options = c("hold_position"), full_width = F) %>%
  row_spec(0, bold = TRUE) %>%
  collapse_rows(columns = 1:2, latex_hline = "major") %>%
  footnote(symbol_title = "", 
         symbol = c("Moderator variables whose 95\\\\% confidence intervals do not cross zero are shown in bold.", 
                     "Hedges' \\\\textit{g} is the response variable for this model"), 
         threeparttable = T, 
         escape = F)
```

@@

![\textbf{The effect of sexual selection on direct, indirect and ambiguous fitness components.} The effect sizes used in this meta-analysis ($n$ = 459) were grouped into either direct, indirect or ambiguous measures of fitness. Overall, effect sizes were more often positive than negative. Predicted average values are presented as a diamond with 95 % CIs for each fitness-relationship category. The estimates presented here are from REML models with the grand mean across all effect sizes ($\beta$ = 0.25) shown as the blue dotted line. Predictions from both Bayesian and REML models can be found in Table S7).\label{forest_plot}](Figures/forest.plot.class.pdf)

![\textbf{The roles of environmental stress and sex.} (a) Sexual selection tends to increase the population mean values of fitness traits, especially for female traits and for populations living under stressful conditions. (b) Under stressful conditions, sexual selection tends to reduce the phenotypic variance in fitness traits, especially for traits measured in females or mixed-sex individuals. The points with error bars show the mean effect sizes and their 95% CIs, determined from a meta-regression fit using restricted maximum likelihood (REML); the point sizes are proportional to the number of effect sizes (see Table S12 and S14). Results from Bayesian meta-regression are shown as posterior prediction density curves, with vertical lines indicating the median.\label{env_sex}](Figures/environment_variance_edit5.pdf)

![\textbf{Tests for publication bias in the dataset.} Tests of publication bias are mixed and suggest publication bias may be present. (a) Inspection and statistical tests of the funnel plot reveal large amounts of heterogeneity in the dataset with asymmetry from increased low-powered, large effect studies. (b) No significant correlation exists between journal impact factor and effect size, (c) additionally there is no significant correlation between effect size and year of publication when testing for the time-lag bias. For (b) and (c) point size is proportional to the precision of the effect size (*i.e.* the inverse of its variance). For (a), the dashed red lines represent the 95 % CIs of the grand mean estimate for all effect sizes and the black dotted and dashed lines depict the 95 % and 99 % CIs for the dataset. The Grey envelopes in (b) and (c) represent the 95 % CI of the linear regression.\label{publication_bias}](Figures/publicationbias.pdf)

![\textbf{PRISMA diagram.} Flow of inclusion and exclusion of studies identified during the literature search, presented as a PRISMA diagram with number of published papers in brackets.\label{prisma_flow}](Figures/PRISMA\ Chart.pdf)
